---
output: github_document
bibliography: inst/REFERENCES.bib
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The hcidata Package

<!-- badges: start -->
<!-- badges: end -->

The goal of hcidata is to provide a collection of datasets from the field of human-computer interaction (HCI).
Each dataset is from an HCI paper, with all fields described and the original publication linked.
All paper authors of included data have consented to the inclusion of their data in this package. 
The datasets include data from a range of HCI studies, such as pointing tasks, user experience ratings, and steering tasks.


## Installation

You can install the development version of hcidata from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("henningpohl/hcidata")
```

## Usage

To use a dataset from this package, first add it to your R project:

```{r}
library(hcidata)
```

You can also inspect the available datasets via:

```{r}
data(package="hcidata")
```

## Included Data

Includes data from:

<div id="refs"></div>

## Contributing
Please create a pull request if you want to add a dataset to this package.
You should hold the rights to release that data and all your coauthors need to agree to the release.
Your data must not contain personal data to be included into hcidata.